Variation in site entropy explains differences in structure-sequence relationships of proteins

### 2015-05-29 manuscript/manuscript.tex
Changed author list
Adding some comments on future edits

\title{Variation in site entropy explains differences in structure-sequence relationships of proteins}
\author{Amir Shahmoradi$^1$, Eleisha L. Jackson$^2$, Claus O. Wilke$^{2*}$}
\begin{document}

@@

\bigskip
\noindent
$^*$Corresponding author\\
%$\phantom{^*}$Email: amir@physics.utexas.edu\\
$\phantom{^*}$Email: wilke@austin.utexas.edu\\
%$\phantom{^*}$Phone:{ \color{red} Need a phone} \\
$\phantom{^*}$Phone: +1 512 232 2459\\

@@

@@

>>>>

\title{Variation in site entropy explains differences in structure-sequence relationships of proteins}
\author{Eleisha L. Jackson$^{2^*}$, Amir Shahmoradi$^{1*}$, Claus O. Wilke$^{2^{**}}$}
\begin{document}

@@

\noindent $^{*}$These authors contributed equally. \\

\bigskip
\noindent
$^{**}$Corresponding author\\
%$\phantom{^*}$Email: amir@physics.utexas.edu\\
$\phantom{^{** }}$Email: wilke@austin.utexas.edu\\
%$\phantom{^*}$Phone:{ \color{red} Need a phone} \\
$\phantom{^{**}}$Phone: +1 512 232 2459\\

@@

Need a section about:
Rate4Site is completely different from the entropy variation and we do not know why. Explain the difference.

@@

Figures that are still needed...
Table 1 - First make a new table with the mean values Entropy
Table 2 - First make a new table with the mean values Rate4Site

\begin{center}
	\begin{tabular}{ | c | c | c |  }
	\hline
	  1 & 2 & 3 \\   \hline	
	 4 & 5 & 6 \\ 	 \hline
	  7 & 8 & 9 \\
	  \hline
	\end{tabular}
\end{center}

Need a two panel figure \\
First plot the mean entropy vs the variance of entropy (then pick points that are in each of the four corners). This is B. I need to circle these by pointing an additional geom point and open circles and put numbers.  \\
Pick these proteins and then plot the distributions. This is A. \\
Basically this figure will highlight the difference between mean entropy and variance in entropy. \\

In the introduction and abstract need to better highlight the two papers (Yeh and Shah) that contradict on the surface and they do not. Hold off on Rate4Site for Now.
